Adaptive evolution with aneuploidy and mutation

### 2022-03-13 ms/ms.tex
small changes

We also plot posterior prediction: we get maximum a posteriori (MAP) estimate of the models, and for each model we execute $10,000$ simulations and plot distribution of time to fixation of \eumt, one of key properties that define the likelihood of the model to fit the data. This visualization helps to see what model fits data better, at least for it MAP parameter vector.

Also, for similar models we plot the posterior distribution of parameters, and joint distributions of parameters and if they are similar we say that the models are interchangeable. We validate it by comparing HDI (highest density interval) of posterior parameters of the models.

@@

 % Fig tau comparisons
%% generated with diff-tau.ipynb
% TODO IK 10_000 reps is mocked, should be rerunned and fixed
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-A.pdf}      
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-B.pdf}      
  \end{subfigure}
  \\
   \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-C.pdf}      
  \end{subfigure}
    \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-D.pdf}      
  \end{subfigure}
    \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-E.pdf}      
  \end{subfigure}
  \\
  \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-F.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-G.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-H.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-I.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-J.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-K.pdf}      
  \end{subfigure}
  \caption{
    \textbf{Single-locus model inference with elevated mutation rate in aneuploid cells.}  \textbf{(A-E)} The inferred posterior distributions of model parameters for the model with different values of $\tau$, the fold-increase in mutation rate in aneuploid cells (\anwt\ and \anmt). When the increase in mutation rate is high, $\tau=10$ and $\tau=100$, the inferred mutation (A) and aneuploidy (B) rate tends to be lower. 
    \textbf{(F-K)} The inferred joint posterior distribution of mutation rate ($\mu$) and aneuploidy rate ($\delta$) with different $\tau$ values (dark purple and bright yellow for low and high density, respectively).
  \label{fig:tau}
  }
  % TODO IK maybe add dashed vertical lines with the same colors to show where the MAP of each distribution is?

>>>>

We also plot posterior predictions: for each model we execute $10,000$ simulations using the MAP parameter estimates and plot the distributions of time to fixation of \eumt, one of key properties of the model likelihood. This visualizes the fit of each model to the data. 
Also, for similar models we plot the marginal and joint posterior distributions of the parameters; if these are similar, we consider the models are interchangeable. We validate this by comparing HDI (highest density interval) of posterior distributions.

@@

 % Fig tau comparisons
%% generated with diff-tau.ipynb
% TODO IK 10_000 reps is mocked, should be rerunned and fixed
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-A.pdf}      
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-B.pdf}      
  \end{subfigure}
  \\
   \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-C.pdf}      
  \end{subfigure}
    \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-D.pdf}      
  \end{subfigure}
    \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-E.pdf}      
  \end{subfigure}
  \\
  \begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-F.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-G.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-H.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-I.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-J.pdf}      
  \end{subfigure}
\begin{subfigure}{0.325\textwidth}
      \includegraphics[width=\textwidth]{../figures/tau-joint-K.pdf}      
  \end{subfigure}
  \caption{
    \textbf{Model with elevated mutation rate in aneuploid cells.}  \textbf{(A-E)} The inferred posterior distributions for models with different values of $\tau$, the fold-increase in mutation rate in aneuploid cells (\anwt\ and \anmt). When the increase in mutation rate is high, $\tau=10$ and $\tau=100$, the inferred mutation (A) and aneuploidy (B) rate tends to be lower. 
    \textbf{(F-K)} The inferred joint posterior distribution of mutation rate ($\mu$) and aneuploidy rate ($\delta$) with different $\tau$ values (dark purple and bright yellow for low and high density, respectively).
  \label{fig:tau}
  }
  % TODO IK maybe add dashed vertical lines with the same colors to show where the MAP of each distribution is?
